\documentclass[line,margin]{res}
    \usepackage[none]{hyphenat}
    \usepackage{textcomp}
    \begin{document}
\name{{\LARGE Randolph Liang}}
\address{randy8@vt.edu | (571) 296-6786 | github.com/kidcharlemagne}
\begin{resume}
	\vspace{-5mm}
	\section{EDUCATION}
	\textbf{Virginia Tech}, {\sl B.S. in Computer Science, minor in Mathematics} GPA: 3.14\hfill Dec 2018\\Blacksburg, VA
	\section{EXPERIENCE}
	\textbf{Leidos}, {\sl Software Engineer Co-Op Intern}\hfill May 2017 | December 2017\\Reston, VA\\\begin{itemize} \itemsep 1pt
	\item Learned branching strategies (Git), team-specific conventions, and agile development practices.
	\item Spearheaded the development of a virtualized network to automatically setup/deploy VM nodes, developed a configuration server in C#, and integrated a multilingual XMPP Android chat client.
	\item Developed a Python GUI using TKinter that dumps user input into a JSON file and feeds it to Scrapy spiders to obtain OSM map data from online sources.
	\end{itemize}
	\section{SKILLS}
	\begin{tabular}{@{}ll}
		\textbf{Programming Languages}: & Java, Python, C, Swift   \\
		\textbf{Operating Systems}:     & GNU/Linux (Debian and RPM), macOS \\
	\end{tabular}
	\section{PROJECTS}
	\textbf{Extensible Shell}, {\sl C}\\ process management for various UNIX commands, job control, and plugin support. Takes line-by-line input from the command line.\\\\
	\textbf{Memory Manager}, {\sl Java}\\ \href{https://github.com/kidcharlemagne/DSA/tree/master/2-3%2B%20Tree} \\memory management package for storing records consisting of songs/artists from a million-song database, relying on a hash table to store handles that point to the song/artist index in the memory manager. Implements a range query using a 2-3+ tree to retrieve songs written by specific artists.\\\\
	\textbf{randyliang.com}, {\sl swift, xcode, UIKit}\\ memory management package for storing records consisting of songs/artists from a million-song database, relying on a hash table to store handles that point to the song/artist index in the memory manager. Implements a range query using a 2-3+ tree to retrieve songs written by specific artists.\\\\
	\textbf{Lyric Bot}, {\sl Python}\\ https://github.com/vinnyoodles/mosaic-layout\\Twitter bot that scrapes lyrics from the web and tweets them every 30 minutes.\\\\
	\textbf{cartera}, {\sl swift, xcode, UIKit, Parse}\\ https://github.com/makersofawesome/cartera\_ios\\\begin{itemize} \itemsep 1pt
	\item Developed an iOS app that allows any user to become an ATM for people who need cash in a hurry for VT Hacks Capital One API category. 
	\item Wrote the networking client wrapper for the Capital One API and the Parse backend using NSURLConnection. 
	\item Implemented view logic following the MVC paradigm using UIKit and Mapkit.
	\end{itemize}
	          
	\ 
\end{resume}
\end{document}
